Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-22 thesis/paper_draft.qmd
reorganise paths (move lib folder outside), rerender

<!-- Write cover page my own -->

@@

\begin{center}
\includegraphics[height=2cm,keepaspectratio]{D:/Github/Recon_Honours_Thesis/assets/monash-logo.png}
\end{center}

@@

```{r library}
library(ggplot2)
library(patchwork)
library(dplyr)
library(tidyr)
library(fable)
library(fabletools)
library(feasts)
library(tsibble)
library(lubridate)
library(knitr)
library(kableExtra)
library(stringr)
library(forcats)
library(tibble)
library(fmsb)

@@

path <- here::here()
knitr::opts_knit$set(root.dir = path)
# setwd(path)
```

@@

<!-- [This is pasted from the Project Description]{style="color:red;"} -->

A collection of time series connected via a set of linear constraints is known as hierarchical time series. Forecasting these series without respecting the hierarchical nature of the data can lead to incoherent forecasts across aggregation levels and, in practice, reduced accuracy. Forecast reconciliation corrects this by adjusting base forecasts to satisfy such constraints. Among modern reconciliation methods, Minimum Trace (MinT) is widely used, however, it requires a good estimate of the forecast error covariance matrix. The current practice is to use the linear shrinkage towards a diagonal target. Furthermore, the covariance estimate is based on 1-step-ahead residuals, then proportionally scale it to approximate the h-step-ahead covariance matrix. This leaves a question of whether this method is appropriate for all real-world applications. We study the shortcomings of current practice and propose alternative covariance estimators, including the NOVELIST estimator (shrinkage towards a soft-thresholded target), PC-adjusted shrinkage (which utilises latent factor structures), and horizon-specific estimators that relax proportional scaling. We evaluate MinT using these covariance estimates for both point and probabilistic reconciliation, and demonstrate their effectiveness and improvements over the shrinkage estimator in a complex, large-hierarchy dataset.

@@

```{r load results}
path_lib <- paste0(path, "/thesis/lib/")

sim_params_S36 <- readRDS(paste0(path_lib, "params_S36_6_1.rds"))
sim_params_S100 <- readRDS(paste0(path_lib, "params_S100_10_3_1_dense.rds"))
sim_params_sparse <- readRDS(paste0(path_lib, "params_S100_10_3_1_sparse46.rds"))

@@

```{r}
tourism_plots <- readRDS("D:/Github/Recon_Honours_Thesis/thesis/tourism_plots.rds")
```

@@

tourism_MSE_results <- readRDS(paste0(path, "/thesis/lib/tourism_MSE_results.rds"))

@@

tourism_uniscores <- readRDS(paste0(path, "./thesis/lib/tourism_uniscore_results.rds"))
tourism_energy <- readRDS(paste0(path, "./thesis/lib/tourism_energyscore_results.rds"))

@@

tourism_coverage95 <- readRDS(paste0(path, "/thesis/lib/tourism_coverage95.rds"))
tourism_W95_level <- readRDS(paste0(path, "/thesis/lib/tourism_W95_level.rds"))

>>>>

<!-- COVER PAGE -->

@@

\begin{center}
\includegraphics[height=2cm,keepaspectratio]{D:/Github/Recon_Honours_Thesis/figs/monash-logo.png}
\end{center}

@@

```{r library}
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(patchwork)
library(fable)
library(fabletools)
library(feasts)
library(tsibble)
library(lubridate)
library(knitr)
library(kableExtra)
library(stringr)
library(forcats)
library(fmsb)

@@

path <- here::here()
path_lib <- paste0(path, "/lib/") # lib folder (sim, empi results)
knitr::opts_knit$set(root.dir = path)
```

@@

A collection of time series connected via a set of linear constraints is known as hierarchical time series. Forecasting these series without respecting the hierarchical nature of the data can lead to incoherent forecasts across aggregation levels and, in practice, reduced accuracy. Forecast reconciliation corrects this by adjusting base forecasts to satisfy such constraints. Among modern reconciliation methods, Minimum Trace (MinT) is widely used, however, it requires a good estimate of the forecast error covariance matrix. The current practice uses linear shrinkage towards a diagonal target. Furthermore, the covariance estimate is based on 1-step-ahead residuals, then proportionally scale it to approximate h-step-ahead covariance matrix. This leaves a question of whether this method is appropriate for all real-world applications. We study the shortcomings of current practice and propose alternative covariance estimators, including the NOVELIST estimator (shrinkage towards a soft-thresholded target), PC-adjusted shrinkage (which utilises latent factor structures), and horizon-specific estimators that relax proportional scaling. We evaluate MinT using these covariance estimates for both point and probabilistic reconciliation, and demonstrate their effectiveness and improvements over the shrinkage estimator in a complex, large-hierarchy dataset.

@@

```{r load results}
sim_params_S36 <- readRDS(paste0(path_lib, "params_S36_6_1.rds"))
sim_params_S100 <- readRDS(paste0(path_lib, "params_S100_10_3_1_dense.rds"))
sim_params_sparse <- readRDS(paste0(path_lib, "params_S100_10_3_1_sparse46.rds"))

@@

<!-- ```{r}
tourism_plots <- readRDS("D:/Github/Recon_Honours_Thesis/thesis/tourism_plots.rds")
``` -->

@@

tourism_MSE_results <- readRDS(paste0(path_lib, "tourism_MSE_results.rds"))

@@

tourism_uniscores <- readRDS(paste0(path_lib, "tourism_uniscore_results.rds"))
tourism_energy <- readRDS(paste0(path_lib, "tourism_energyscore_results.rds"))

@@

tourism_coverage95 <- readRDS(paste0(path_lib, "tourism_coverage95.rds"))
tourism_W95_level <- readRDS(paste0(path_lib, "tourism_W95_level.rds"))
